Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1231 at $z$=0.654

### 2016-06-21 WRITEUP/ms.tex
update LIR, explains HVI bands extents

\title{Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1123 at $z$=0.654}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\subsubsection{Interpretation of the source plane morphology} \label{sec:caveat}
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient across the source plane, which is
indicative of a disk-like galaxy.
Additional support to the disk conjecture
can be found in the double-horned line profile (\Fig{CO21spec})
and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
C06 also find that the reconstructed source plane emission in optical-NIR
is best-reproduced using a $n$\,=\,1 Sersic profile.
We thus interpret RXJ1131 to be a disk galaxy.

% the companion
One other interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
(component F in their paper) $\sim$2.4\,kpc away from the AGN host galaxy,
and C06, who find evidence for an interacting galaxy near RXJ1131.
Spatially, the red velocity component of the CO emission
also coincides with this component F. It is therefore evident that we
detect \bco emission in the companion galaxy.
To quantify the type of merger (major v.s. minor) conventionally with a mass
ratio, we decompose the total line flux into two components:
one from RXJ1131 and the other from its companion.
Since the companion is only detected in the red-most channel, we
use the best-fit flux densities and magnification factors obtained
from the model of this channel to derive the intrinsic gas mass in the companion.
Without direct \rot{1}{0} measurements, we derive \rot{1}{0} intensity
assuming a brightness temperature ratio of $r_{\rm 21}$\,=\,1, which was chosen
solely to facilitate a comparison with other U/LIRGs. 
% also ULIRGs are found to be thermalized up to Jup = 3 or 4, but not needed to say here
For the same reason, we adopt a luminosity-to-mass conversion factor of
\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne. This yields a gas mass
$M_{\rm gas}$ of (1.92\pmm0.09)\,\E{9} \Msun. 
%statistical unc. only (i.e. draw from distributions of on mag. factor & intrinsic flux)
For the molecular gas mass in RXJ1131, we derive
its intrinsic line flux over the FWZI linewidth
using the respective magnification
factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing.
This yields $I_{\small \bco}$\,=\,2.93\pmm0.70 Jy\,\kms,
where the uncertainty includes those on
the magnification factors.
Adopting the same brightness temperature ratio and \alphaco\ as
used for the companion, this corresponds to a gas mass of
$M_{\rm gas}$\,=\,(1.38\pmm0.33)\,\E{10} \Msun,
implying a gas mass ratio of $\sim$7:1 between RXJ1131 and its companion.
We thus classify the system to be a ``wet-wet'' minor merger according to
the classification scheme/convention commonly used in literature.

@@

\subsubsection{Spatial extent and differential lensing} \label{sec:differential}
In the image plane shown in  \Fig{CO21mom}, the redshifted component is 
cospatial with the Einstein Ring seen in the
optical image, with most of its apparent flux originating from the lensed arc
in the southeast, whereas the blue component is predominately coming from
solely the lensed arc. To further illustrate this, we show the
channel maps of 21.5\,\kms width and a spatial spectra map of 1\farcs5 resolution in
\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures
show that emission
is present to the west, peaking toward the lensing arc (black crosses in
\Fig{chanmap}) in the red wing, and shifts to the east with decreasing velocity
(blue wing).
This is consistent with the source plane positions in our models and 
suggests that the 
overall CO emitting region is extended.

@@

\input{table_magFactor}
Similar to previous studies of RXJ1131, where
differential lensing across {\it HST}
$H$-, $V$-, and $I$-band has been detected with a
magnification factor decreasing from 10.9 to 7.8 (C06),
the highly asymmetric \bco line profile suggests that
differential lensing is also non-negligible for CO,
causing the redshifted emission to be apparently much brighter than the
blueshifted component and the asymmetric line profile.   
To first order, this can be explained by the difference in magnification factor which
varies from 8.7 to 3.1 across the \bco line (\Tab{model}).  % also because of a contribution from the companion in the observed, lensed spectrum
Such an effect (difference in $\mu_{\rm L}$ across channels) is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing 
emission mainly originates near the cusp 
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and 
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
is $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively, 
implying an intrinsically symmetric line profile.

\subsection{\bco Kinematics} % DONE
A clear velocity gradient and a high
velocity dispersion ($\gtrsim$400\,\kms) near the central region
is seen in \Fig{CO21highO}. While beam smearing is inevitably the
dominant factor in the observed velocity dispersion
at the spatial resolution of this data, the exceedingly
high velocity dispersion may hint
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the large gas
content. A velocity gradient across the source plane in \Fig{model} is also
found in our lens model. This further supports the idea of a
kinematically-ordered galaxy, but its emission has been lensed differentially.
In this scenario, RXJ1131 is a disrupted disk galaxy hosting an optically
bright quasar and is in the process of merging.

@@

The asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is not equivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disc peaks.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
lens model (C06; converted to
our cosmology).
We note that the source plane half-light radius varies substantially with
wavelength. In particular, the half-light radius is found to be
$\sim$\,4kpc and $\sim$7\,kpc in $V$-band
\citep{Brewer08a} and $H$-band (C06), respectively.
This discrepancy arises owing to the exclusion of the more
diffused emission in $V$-band (rest-frame UV),
which traces young massive stars.
The $V$-band compactness may be explained in part
due to the fact that its emission is
more susceptible to dust extinction than other bands.
On the other hand, the molecular gas (fuel for \SF) is more compact
than the more evolved stellar population, as traced by $I$ and $H$-bands.
This is consistent with the picture that stars diffuse outward
after their formation \citep{Calzetti01a}.

Using our estimate of $V_{\rm rot}$, we find a dynamical mass of
$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$\,=\,17\E{10}\,\Msun enclosed
within the CO-emitting region. If we instead consider the
line peak separation from the
\bco line profile $\Delta v_{\rm sep}/2 \sim$200\,\kms, we find
$M_{\rm dyn}$\,sin$^2 i$\,($<$\,6\,kpc$)$\,=\,5.8\E{10}\,\Msun.
We correct for the inclination effect using the
morphological axial ratio from the reconstructed image (Figure 3 in C06), where
the minor axis is 1\farcs8 and the major axis is 3\farcs25.
We thus find an inclination angle of 56.4\degr, which is consistent with the
observed unobscured AGN and an observable double peak line profile.
The dynamical mass is then
8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
Since this quantity is derived under the assumption that the gas is
virialized, which is highly unlikely given the velocity dispersion and the
presence of a close companion, our estimate is
at most a lower limit.

\subsection{SED modeling} \label{sec:SED}  % DONE
We fit dust SED models to the
24\,\micron$-$2.2\,mm photometry in \Fig{SED}, where we also
include the IRAS 60\,$\micron$ and 100\,$\micron$ upper limits
to constrain the dust peak.
The fit is performed with the code
\ncode{mbb\_emcee} \citep[\eg][]{Riechers13a,Dowell14a}, which samples the posterior
using an MCMC approach and uses instrumental
response curves to perform color correction on-the-fly.
The SED model consists of a modified-blackbody
function with a power-law attached to the
Wien side to account for an excess in the MIR owing to warm,
small dust emission.
% Previous studies find that in the absence of mid-IR data, a powerlaw slope
% of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, % for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
%
%We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
%uncertainties for the PdBI continuum in our fitting procedure.
The model is thus described by five free parameters: the rest-frame characteristic dust
temperature (T$_{d}$), the emissivity index ($\beta$), the power-law index
($\alpha$), the flux normalization at 500\,$\micron$ ($f_{\rm norm}$), and
the observed-frame wavelength at which the emission
becomes optically thick ($\lambda_{0}$). We impose
an upper limit of 100\,K on $T_d$, a Gaussian prior centered around
$\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and an upper limit of
1000\,$\micron$ on $\lambda_0$.
We check for chain convergence by requiring the autocorrelation
length of each parameter to be less than the number of steps
taken for the burn-in phase (which are then discarded).
Here we report the means % modes in log file
% summary statistics (global mode (where min. chi),
% marginal mode (in log file), posterior median (instead of posterior means;
% need to compute)
and the 1$\sigma$ confidence interval in the marginal PDFs
as the best-fit parameters, as listed in \Tab{SED}.

@@

A fit including the MIR 24\,$\micron$ photometry
is likely an upper limit on the \fir luminosity arising from the starburst
in the AGN host galaxy.
% since the fit include contribution from the AGN (through power-law to MIR)
If we instead fit for a model excluding the 24\,$\micron$ constraint,
two major consequences are immediately apparent.
First, the power-law index is poorly-constrained (see \Tab{SED}).
Second, the steep power-law implies a small contribution
from the power-law regime
to the total IR luminosity as compared to the graybody.
Thus, the \fir luminosity in
this model should, in principle, corresponds to a
lower limit on the cold dust emission.
Using the best-fit parameters
for this model, we find a total IR luminosity
\LIR (rest-frame 8\,$-$\,1000\,\micron) of 8.14\petm{2.64}{2.80}\E{12}\,\Lsun,
a \fir luminosity \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a
dust mass $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun.
Taken at face value, this implies a \LFIR-to-\LIR ratio
of $\sim$58\pmm BLAH\%.
Again, the inferred quantities are uncorrected for lensing.
%The best-fit SEDs are shown in \Fig{SED} and the
% resulting parameters are listed in \Tab{SED}.

The dust temperature from both models is similar to that of
ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K; \citealt[hereafter C13]{Combes13a}).
We note the \fir luminosity is comparable in both models, which is
not surprising given the lack of constraints in the MIR. In fact, the
\fir luminosity from the second model is slightly higher than the former, but
consistent within the uncertainties.
For the subsequent analysis, we adopt the physical quantities
from the former (\ie with constraints at 24\,\micron).
The choice of SED model does not affect
the derived star formation rate (SFR) given the similar \fir luminosity.
Yet, the dust mass is higher in the former (but consistent within the
uncertainties), and thus the gas-to-dust ratio in \Sec{properties}
should be considered as an estimate.
We correct for lensing using the median magnification
factor $(\mu_{\rm L}\eq5.5)$
from the CO lens models. This yields a \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun.
Assuming a Salpeter initial
mass function \citep{Salpeter55a}, we find a
SFR of (120\pmm63)\,\Msun\,yr\pmOne using the
standard conversion \citep{Kennicutt98a}.

@@

To place RXJ1131 in context of existing studies,
we compare its properties
with those reported by C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements.
Since C13 adopt a different definition of
\LFIR (40\,$-$\,500\,\micron)\footnote{We also note that the
\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes.},
we derive the \fir luminosity following this convention.
This yields $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.
This implies that RXJ1131 is considered a LIRG in regard to their
sample, and consequently, the SFR of RXJ1131 is lower
(cf. SFR\,$>$\,200, with an average of 1200 in C13).
If we instead adopt the
more generally used definition for the total IR luminosity,
calculated using 8\,$-$\,1000\,\micron, RXJ1131 would be
considered a ULIRG given its lensing-corrected
total IR luminosity of $\sim$2\E{12}\,\Lsun.

\subsection{Gas properties} \label{sec:properties}
In this section, we derive the gas properties of RXJ1131 based on \bco,
and compare the derived quantities against those reported by
C13, where their results are based on \bco and \rot{4}{3} line observations on the IRAM 30-m dish.

>>>>

\title{Molecular Gas Dynamics of the lensed wet-merger RXSJ1131-1231 at $z$=0.654}
\author{T. K. Daisy Leung and Dominik A. Riechers}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\subsubsection{Interpretation of the source-plane morphology} \label{sec:caveat}
The reconstructed source locations in \Fig{model} demonstrate
an intrinsic velocity gradient across the source plane, which is
indicative of a kinematically-ordered disk-like galaxy. 
Additional support to the disk conjecture
can be found in the double-horned line profile (\Fig{CO21spec})
and the observed (image plane) velocity field (\Fig{CO21highO}). Furthermore,
C06 also find that the reconstructed source plane emission in optical-NIR
is best-reproduced using a $n$\,=\,1 Sersic profile.
We thus interpret RXJ1131 to be a disk galaxy.

% the companion
One other interesting result from our lens model is that a better fit is
found for the red-most channel if we add a second source component (see
top left panel in \Fig{model}). This is consistent with previous results
reported by \citet{Brewer08a}, who find an optically faint companion
(component F in their paper) $\sim$2.4\,kpc away from the AGN host galaxy,
and C06, who find evidence for an interacting galaxy near RXJ1131.
Spatially, the red velocity component of the CO emission
also coincides with this component F. It is therefore evident that we
detect \bco emission in the companion galaxy.
To quantify the type of merger (major v.s. minor) conventionally with a mass
ratio, we decompose the total line flux into two components:
one from RXJ1131 and the other from its companion.
Since the companion is only detected in the red-most channel, we
use the best-fit flux densities and magnification factors obtained
from the model of this channel to derive the intrinsic gas mass in the companion.
Without direct \rot{1}{0} measurements, we derive \rot{1}{0} intensity
assuming a brightness temperature ratio of $r_{\rm 21}$\,=\,1, which was chosen
solely to facilitate a comparison with other U/LIRGs. 
% also ULIRGs are found to be thermalized up to Jup = 3 or 4, but not needed to say here
For the same reason, we adopt a luminosity-to-mass conversion factor of
\alphaco\,=\,0.8 (K \kms pc$^2$)\pmOne. This yields a gas mass
$M_{\rm gas}$ of (1.92\pmm0.09)\,\E{9} \Msun. 
%statistical unc. only (i.e. draw from distributions of on mag. factor & intrinsic flux)
For the molecular gas mass in RXJ1131, we derive
its intrinsic line flux over the FWZI linewidth
using the respective magnification
factors listed in \Tab{model}, which to
first order takes into account effect of differential lensing.
This yields $I_{\small \bco}$\,=\,2.93\pmm0.70 Jy\,\kms,
where the uncertainty includes those on
the magnification factors.
Adopting the same brightness temperature ratio and \alphaco\ as
used for the companion, this corresponds to a gas mass of
$M_{\rm gas}$\,=\,(1.38\pmm0.33)\,\E{10} \Msun,
implying a gas mass ratio of $\sim$7:1 between RXJ1131 and its companion.
We thus classify the system to be a ``wet-wet'' minor merger according to
the classification scheme commonly used in literature.

@@

\subsubsection{Spatial extent and differential lensing} \label{sec:differential}
In the image plane shown in  \Fig{CO21mom}, the redshifted component is 
cospatial with the Einstein Ring seen in the
optical image, with most of its apparent flux originating from the lensed arc
in the southeast, whereas the blue component is predominately coming from
solely the lensed arc. To further illustrate this, we show the
channel maps of 21.5\,\kms width and a spatial spectra map of 1\farcs5 resolution in
\Fig{chanmap} and \Fig{spatialSpec}, respectively. The figures
show that emission
is present to the west, peaking toward the lensing arc (black crosses in
\Fig{chanmap}) in the red wing, and shifts to the east with decreasing velocity
(blue wing).
This is consistent with the source plane positions in our models and 
is suggestive of an extended CO emitting region.

@@

\input{table_magFactor}
Similar to previous studies of RXJ1131, where
differential lensing across {\it HST}
$V$-, $I$-, and $H$-band has been detected with a
magnification factor decreasing from 10.9 to 7.8 (C06),
the highly asymmetric \bco line profile suggests that
differential lensing is also non-negligible for CO,
causing the redshifted emission to be apparently much brighter than the
blueshifted component and the asymmetric line profile.   
To first order, this can be explained by the difference in magnification factor which
varies from 8.7 to 3.1 across the \bco line (\Tab{model}).  % also because of a contribution from the companion in the observed, lensed spectrum
Such an effect (difference in $\mu_{\rm L}$ across channels) is consistent with the source plane
positions relative to the caustics in \Fig{model}, where the red wing 
emission mainly originates near the cusp 
of the caustic and the blue wing emission is located beyond the caustics.
In fact, the intrinsic line flux of the redshifted and 
blueshifted emission in RXJ1131 (after subtracting a contribution from the companion)
is $I_{\small \bco}$\,=\,1.26\pmm 0.23 Jy\,\kms and 1.25\pmm0.23 Jy\,\kms, respectively, 
implying an intrinsically symmetric line profile. This is consistent with the source-plane
velocity gradient in our lens model (see \Sec{caveat}). 
% The difference in magnification factors between CO and optical-to-NIR emission
% may further indicate that the CO emitting region is more extended than .

\subsection{\bco Kinematics}
A clear velocity gradient and a high
velocity dispersion ($\gtrsim$400\,\kms) near the central region
is seen in \Fig{CO21highO}. While beam smearing is inevitably the
dominant factor in the observed velocity dispersion
at the spatial resolution of this data, the exceedingly
high velocity dispersion may hint
at potential perturbations from the AGN, or internal turbulence due to
interactions with the companion, and/or instability due to the large gas
content. 
Therefore, in this scenario, RXJ1131 is 
likely a disrupted disk galaxy hosting an optically
bright quasar and is in the process of merging.

@@

The asymptotic velocity ($V_{a}$) -- an extrapolation of the model
out to radius beyond the disk scale-length and half-light radius --
is not equivalent to maximum observed velocity ($V_{\rm max}$),
which is commonly used in literature to parameterize disc rotation.
The arctangent model is most commonly used in studies of the
Tully-Fisher relation, where an extrapolation to V$_{2.2}$ (velocity
at 2.2 disc scale-length or $\sim$1.375 half-light radius,
or $\sim$0.7$R_{\rm opt}$\footnote{Radius enclosing 83\% of the light
distribution.}) is typically adopted
as the rotation velocity ($V_{\rm max}$ in their
terminology) since this corresponds to the radius at which the velocity
of a pure exponential disk peaks \citep{Courteau97b}.
We here adopt the maximum {\em observed} velocity
$V_{\rm rot}$\,=\,345\,$\pm$\,55\,\kms at 6\,$\pm$\,3\,kpc from the % line center velo of the reddest channel slice, unc = slice width
dynamical center as a proxy to the rotation velocity.
This radius corresponds to $\sim$0.6$R_e$, where $R_e$ is the half-light
radius $\sim$10.3\,kpc inferred from the {\it HST} $I$-band
lens model (C06; converted to
our cosmology).
We note that the source plane half-light radius varies substantially with
wavelength. In particular, the half-light radius is found to be
$\sim$\,4\,kpc and $\sim$7\,kpc in $V$-band
\citep{Brewer08a} and $H$-band (C06), respectively.
The CO gas is thus of similar spatial
extent as $H$ and $I$-bands.

In the rest-frame, 
emission in the observed $H$-band corresponds to NIR emission, 
tracing radiation from the accretion disk surrounding
the central AGN and also from old and evolved stellar populations; 
$I$-band corresponds to roughly the optical $V$-band, tracing stellar radiation from
existing, less massive (\ie longer-lasting) stars;
$V$-band corresponds to roughly $U$-band,  tracing radiation from massive young stars 
in the host galaxy. Hence,
the $V$-band compactness may be explained in part
due to the fact that its emission is
more susceptible to dust extinction than in other bands and/or 
a central starburst caused by higher 
concentrations of star-forming gas towards the central regions -- owing to
gravitational perturbations induced
from interactions with the companion
\citep[\eg][]{DiMatteo05a}.
The rest-frame NIR emission is likely to be
dominated by evolved stars since 
the AGN is located at $\sim$0\farcs016 inside the central region % and R_H is 7 kpc
of the host galaxy \citep{Sluse06a}, implying a compact accretion disk. 
This is consistent with the picture that old stars form first and constitute the bulge component  
of a spiral galaxy and that nuclear starbursts are triggered in mergers.

% assuming virialized gas
Using $V_{\rm rot}$ estimate from the modeling, we find a dynamical mass of
$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 17\E{10}\,\Msun enclosed
within the CO-emitting region. If we instead consider the
\bco line peak separation $(\Delta v_{\rm sep}/2 \sim$200\,\kms$)$ as the rotation velocity, we find
$M_{\rm dyn}$\,$\sin^2 i$\,$(<$\,6\,kpc$)$ = 5.8\E{10}\,\Msun.
We correct for the inclination effect using the
morphological axial ratio ($a/b\sim$1\farcs8 / 3\farcs25) 
from the reconstructed image (Figure 3 in C06), yielding
an inclination angle of 56.4\degr, which is consistent with the
observed unobscured AGN and an observable double peak line profile.
The dynamical mass is then
8.3\E{10}\Msun\,$<$\,$M_{\rm dyn}$($<$6\,kpc)\,$<$\,25\E{10}\Msun.
Since this quantity is derived under the assumption that the gas is
virialized, which is highly unlikely given the velocity dispersion and the
presence of a close companion, our estimate is
at most an upper limit.

%% using disk model

\subsection{SED modeling} \label{sec:SED}  % DONE
We fit dust SED models to the
24\,\micron$-$2.2\,mm photometry in \Fig{SED}, where we also
include the IRAS 60\,$\micron$ and 100\,$\micron$ upper limits
to constrain the dust peak.
The fit is performed with the code
\ncode{mbb\_emcee} \citep[\eg][]{Riechers13a,Dowell14a}, which samples the posterior
using an MCMC approach and uses instrumental
response curves to perform color correction on-the-fly.
The SED model consists of a modified-blackbody
function with a power-law attached to the
Wien side to account for an excess in the MIR owing to warm,
small dust emission.
% Previous studies find that in the absence of mid-IR data, a powerlaw slope
% of $\alpha$ = 2 is consistent with SB and slightly more shallow, $\sim$1.5, % for SB/AGN composite systems (Blain et al., 2003; Casey, 2012; Koss et al., 2013).
%
%We add $\sim$15\% calibration uncertainties in quadrature to obtain the total
%uncertainties for the PdBI continuum in our fitting procedure.
The model is thus described by five free parameters: the rest-frame characteristic dust
temperature (T$_{d}$), the emissivity index ($\beta$), the power-law index
($\alpha$), the flux normalization at 500\,$\micron$ ($f_{\rm norm}$), and
the observed-frame wavelength at which the emission
becomes optically thick ($\lambda_{0}$). We impose
an upper limit of 100\,K on $T_d$ (commonly BLAH in ULIRGs; CITE), 
a Gaussian prior centered around
$\mu$\,=\,1.9 with $\sigma$\,=\,0.3 on $\beta$, and an upper limit of
1000\,$\micron$ on $\lambda_0$.
We check for chain convergence by requiring the autocorrelation
length of each parameter to be less than the number of steps
taken for the burn-in phase (which are then discarded).
Here we report the means % modes in log file
% summary statistics (global mode (where min. chi),
% marginal mode (in log file), posterior median (instead of posterior means;
% need to compute)
and the 1$\sigma$ confidence interval in the marginal PDFs
as the best-fit parameters, as listed in \Tab{SED}.

@@

A fit including the MIR 24\,$\micron$ photometry
is likely an upper limit on the \fir luminosity arising from the starburst
in the AGN host galaxy.
% since the fit include contribution from the AGN (through power-law to MIR)
If we instead fit for a model excluding the 24\,$\micron$ constraint,
two major consequences are immediately apparent.
First, the power-law index is poorly-constrained (see \Tab{SED}).
Second, the steep power-law implies a small contribution
from the power-law regime
to the total IR luminosity as compared to the graybody.
Thus, the \fir luminosity in
this model should, in principle, correspond to a
lower limit on the cold dust emission.
Using the best-fit parameters
for this model, we find a total IR luminosity
\LIR (rest-frame 8\,$-$\,1000\,\micron) of 9.71\petm{6.14}{-6.05}\E{12}\,\Lsun,
a \fir luminosity \LFIR of 4.72\petm{2.54}{2.26}\E{12}\,\Lsun and a
dust mass $M_{\rm dust}$ of 11\petm{5}{6}\E{8}\,\Msun, uncorrected for lensing.
Taken at face value, this implies a FIR-to-IR luminosity ratio
of $\sim$58\pmm35\%.
%The best-fit SEDs are shown in \Fig{SED} and the
% resulting parameters are listed in \Tab{SED}.

The dust temperature from both models is similar to that of
ULIRGs at 0.6\,$<$\,$z$\,$<$\,1.0 (54\,$\pm$\,5\,K; \citealt[hereafter C13]{Combes13a}).
We note the \fir luminosity is comparable in both models, which is
not surprising given the lack of constraints in the MIR. 
For the subsequent analysis, we adopt the physical quantities
from the first model (\ie with constraints at 24\,\micron).
The choice of SED model does not affect
the derived star formation rate (SFR) given the similar \fir luminosity.
Yet, the dust mass is higher in the former but consistent within the
uncertainties.
We correct for lensing using the median magnification
factor $(\mu_{\rm L}\eq5.5)$
from the CO lens models. This yields a
 \LFIR of $($6.9\pmm3.6$)$\E{11}\,\Lsun
 and 
 a total IR luminosity of $\sim$1.5\E{12}\,\Lsun,  implying RXJ1131 is a ULIRG.
Assuming a Salpeter initial
mass function \citep{Salpeter55a}, we find a
SFR$_{\rm FIR}$ of (120\pmm63)\,\Msun\,yr\pmOne using the
standard conversion \citep{Kennicutt98a}.

@@

\subsection{Gas properties} \label{sec:properties}
In this section, we derive the gas properties of the merger  
based on \bco and compare with those reported by
C13, which is the largest sample of
IR-luminous galaxy at similar redshift
(0.6\,$<$\,$z$\,$<$\,1.0) with CO measurements\footnote{The
\fir luminosity in C13 is derived based on 60\,$\micron$ and 100\,$\micron$ IRAS fluxes,
and using a different definition of
\LFIR: rest-frame 40\,$-$\,500\,\micron. Following this convention, 
we find a \fir luminosity of 
\LFIR = $($8.8\pmm0.4$)$\E{11}$(\mu_{\rm L}$/5.5$)\pmOne$\,\Lsun and
a SFR of $($150\pmm 70$)$\,\sfrU.}.
% the SFR of RXJ1131 is lower (cf. SFR\,$>$\,200 \Msun yr\pmOne, with an average of 1200 in C13).
We note their results are based on \bco and \rot{4}{3} line observations on the single-dish
IRAM 30-m.
